ShrinkNets

### 2018-01-06 paper/paper.tex
Update plots and add some explanation for the generalization

The results in the figure show that ShrinkNets finds better networks with fewer
training iterations than the other methods, because it achieves higher median 
and less variable accuracies. Despite the simple nature of this experiment, we
believe that the results generalize to more complex search methods.

>>>>

The results in the figure show that ShrinkNets finds better networks with fewer
training iterations than the other methods, because it achieves higher median 
and less variable accuracies. Despite the simple nature of this experiment, we
believe that the results generalize to more complex search methods; mainly
because our solution reduce the dimensionality of the space they have to
explore.
